---
title: "First Bookdown document"
author: "Dr Greig Russell"
date: "1 January 2017"
output:
  bookdown::gitbook:
    config:
      edit: https://github.com/GreigR/Bookdown_trial/edit/master/%s
  bookdown::word_document2: default
documentclass: book
bibliography: trial.bib
repo: https://github.com/GreigR/Bookdown_trial
biblio-style: apalike
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Bookdown trial

This document will be used to build a "book", which will be a single part document in the first instance, leading to a PDF & Word document output [@teece1997dynamic].

\tableofcontents

##Including tables

```{r cars, echo = FALSE, results = "asis"}
library(knitr)
kable(head(mtcars[1:4]), digits = 2, booktabs = TRUE, caption = "Table example")
```

## Including Plots

@covin1989strategic and you can also embed plots, for example:

```{r pressure, echo=FALSE, fig.cap = "Plot of pressure"}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot see table \@ref(tab:cars).

#References{-}

